BERT Model Compression and Weight Sharing

### 2019-05-13 paper/paper.tex
Acknowledgments
Fix second-half of edits

We list a few methods of parameterizing the distortion step. 
\paragraphdot{Pruning} Consider a parameter vector $\bvartheta$, let
  $t_p$ be the $p$-th quantile of the vector $\bvartheta$. Then \[
  \prune(\bvartheta; p) = \one(|\bvartheta| > t_p) \odot \bvartheta
  \]
  be the vector where values in $\bvartheta$ below $t_p$ are zeroed.

@@

% \subsection{Knowledge Distillation}

% Example Structure:

% \begin{itemize}
% \item What is the formal definition of your problem?
% \item What is the precise mathematical model you are using to represent it? In
% almost all cases this will use the probabilistic language from class, e.g.
%   \begin{equation}
%   z \sim {\cal N}(0, \sigma^2)\label{eq:1}
% \end{equation}
% But it may also be a neural network, or a non-probabilistic loss,
% \[ h_t \gets \mathrm{RNN}(x_{t}, h_{t-1} )\]

% This is also a good place to reference a diagram such as Figure~\ref{fig:diagram}.

% \item What are the parameters or latent variables of this model that you plan
% on estimating or inferring? Be explicit. How many are there? Which are you
% assuming are given? How do these relate to the original problem description?
% \end{itemize}

% \begin{figure}
%   \centering
%   \missingfigure[figheight=8cm]{}
%   \caption{\label{fig:diagram} This is a good place to include a diagram
%   showing how your model works. Examples include a graphical model or a neural
%   network block diagram.}
% \end{figure}

% \subsection{Knowledge Distillation}

% Example Structure:

% \begin{itemize}
% \item What is the formal definition of your problem?
% \item What is the precise mathematical model you are using to represent it? In
% almost all cases this will use the probabilistic language from class, e.g.
%   \begin{equation}
%   z \sim {\cal N}(0, \sigma^2)\label{eq:1}
% \end{equation}
% But it may also be a neural network, or a non-probabilistic loss,
% \[ h_t \gets \mathrm{RNN}(x_{t}, h_{t-1} )\]

% This is also a good place to reference a diagram such as Figure~\ref{fig:diagram}.

% \item What are the parameters or latent variables of this model that you plan
% on estimating or inferring? Be explicit. How many are there? Which are you
% assuming are given? How do these relate to the original problem description?
% \end{itemize}

% \begin{figure}
%   \centering
%   \missingfigure[figheight=8cm]{}
%   \caption{\label{fig:diagram} This is a good place to include a diagram
%   showing how your model works. Examples include a graphical model or a neural
%   network block diagram.}
% \end{figure}

@@

@@

For knowledge distillation experiments, we use various configurations of the
student network: \paragraphdot{LSTM} We use a one-layer LSTM network with hidden
dimension $H=200$. We first embed the one-hot representation of tokens, and we
feed the embeddings through an LSTM. We then map the last hidden state of the
LSTM through a linear layer for classification.  \paragraphdot{CNN} We use an
implementation\footnote{\url{https://github.com/jfilter/cnn-text-classification-pytorch/blob/master/cnn_text_classification/model.py}}
of \citet{kim2014convolutional} with kernel sizes $(3,4,5)$, hidden size
$H=300$, no dropout, and $20$ kernels for each kernel size.\footnote{These are
default in the implementation we used.}

@@

We show our results in \Cref {tab:deeptwist_results,tab:kd_results}. In the top
pane of \Cref {tab:deeptwist_results}, we show the result of various
DeepTwist-based compression techniques on the sentiment classification task,
SST-2, stratifying by method and then by parameter of the method. Difference
pruning, pruning, and rank reduction are implemented as \emph{distortion by
layer} (see \Cref{sec:model}), where as ``difference pruning (global)''
indicates difference pruning, but pooling all parameter values from all layers.
The bottom pane of \Cref{tab:deeptwist_results} shows the performance on QQP of
some competitive-performing model setups on SST-2, which are all
difference-pruning based. In \Cref{tab:kd_results}, we present some knowledge
distillation experiments, with the student network being an LSTM or a CNN, with
or without dropout \citep{kim2014convolutional}.

@@

\begin{figure*}[htb]
\centering
\includegraphics[width=\textwidth]{../figs/kd_lstm_training.png}
\caption{Training loss (left), val. loss (middle), and val. accuracy
(right) for LSTM KD}
\label{fig:kdlstmloss}
\end{figure*}

@@

As expected, pruning a higher proportion of the weights decreases performance,
but we are happily surprised at the relatively low magnitude of this effect even
at high prune rates. Pruning with a global threshold rather than in a
stratified way produces distinctly worse results. We suspect this is due to
weights in different layers having different magnitudes, making a global
threshold have an undue effect on layers whose weights tend to be smaller. We
confirm this heterogeneity in \cref{fig:weightsbylayer}.

@@

>>>>

We list a few methods of parameterizing the distortion step. 
\paragraphdot{Pruning} Consider a parameter vector $\bvartheta$, let
  $t_p$ be the $p$-th quantile of the vector $\bvartheta$. Then \[
  \prune(\bvartheta; p) = \one(|\bvartheta| > t_p) \odot \bvartheta
  \]
  is the vector where values in $\bvartheta$ below in absolute magnitude $t_p$
  are zeroed.

@@

@@

For knowledge distillation experiments, we use various configurations of the
student network: \paragraphdot{LSTM} We use a one-layer LSTM network with hidden
dimension $H=200$. We first embed the one-hot representation of tokens, and we
feed the embeddings through an LSTM. We then map the last hidden state of the
LSTM through a linear layer for classification.  \paragraphdot{CNN} We use an
implementation\footnote{\url{https://github.com/jfilter/cnn-text-classification-pytorch/blob/master/cnn_text_classification/model.py}}
of \citet{kim2014convolutional} with kernel sizes $(3,4,5)$, hidden size
$H=300$, no dropout and 50\% dropout, and $20$ kernels for each kernel
size.\footnote{These are default in the implementation we used.}

@@

@@

We show our results in \Cref {tab:deeptwist_results,tab:kd_results}. In the top
pane of \Cref {tab:deeptwist_results}, we show the result of various
DeepTwist-based compression techniques on the sentiment classification task,
SST-2, stratifying by method and then by parameter of the method. Difference
pruning, pruning, and rank reduction are implemented as \emph{distortion by
layer} (see \Cref{sec:model}), where as \emph{difference pruning (global)}
indicates difference pruning, but pooling all parameter values from all layers.
The bottom pane of \Cref{tab:deeptwist_results} shows the performance on QQP of
some competitive-performing model setups on SST-2, which are all
difference-pruning based. In \Cref{tab:kd_results}, we present some knowledge
distillation experiments, with the student network being an LSTM or a CNN, with
or without dropout \citep{kim2014convolutional}.

@@

\begin{figure*}[htb]
\centering
\includegraphics[width=\textwidth]{../figs/kd_lstm_training.png}
\caption{Training loss (left), val. loss (middle), and val. accuracy
(right) plotted against number of batches of training for LSTM KD}
\label{fig:kdlstmloss}
\end{figure*}

@@

As expected, difference pruning a higher proportion of the weights decreases
performance, but we are happily surprised at the relatively low magnitude of
this effect even at high prune rates. Pruning with a global threshold rather
than in a stratified way produces distinctly worse results. We suspect this is
due to weights in different layers having different magnitudes, making a global
threshold have an undue effect on layers whose weights tend to be smaller. We
confirm this heterogeneity in \cref{fig:weightsbylayer}.

@@

We thank Alexander M. Rush and the Harvard CS 287 community, without whom
this work would not have been possible.
